---
title: "Introduction to thePlot"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to thePlot}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(qacPlot)
```

The purpose of the **qacPlot** package is to help users quickly identify suitable plot types and visualize variables they are interested in. The only function `thePlot` can handle univariate, bivariate and multivariate graphs of a dataset based on variable types (categorical or quantitative). 


## Example Dataset 
Let’s use our favorite one **mtcars** as an example. 
```{r message = FALSE, warning = FALSE}
data(mtcars)
```

### Data Management 
Since `thePlot` rely on the type of variables (categorical or quantitative) for selecting plots, you will need to manage the variables you are using `thePlot` for before using the function. 

Typically, you should pay attention to numeric variables that are supposed to be **categorical** in the dataset. For example, the **cyl** variable in **mtcars** should be a categorical variable, but its class is numeric. 

You can copy the following codes to manage the variables in mtcars:

```{r, message = FALSE, warning = FALSE}
mtcars$cyl <- as.factor(mtcars$cyl)
mtcars$vs <- as.factor(mtcars$vs)
mtcars$am <- as.factor(mtcars$am)
mtcars$gear <- as.factor(mtcars$gear)
```

## Let's Plot!
Now we can start plotting with `thePlot`. Let's take a look at univariate, bivariate, and multivariate graphs one by one.

#### Univariate 
When you only want to visualize one variable, you need to specify the data frame and the variable. 
**thePlot(mydata, Variable1)**

```{r, message = FALSE, warning = FALSE}
thePlot(mtcars, am)
thePlot(mtcars, mpg)
```

#### Bivariate
If you are interested in the relationship between two variables, you can follow this syntax:
**thePlot(mydata, ExplanatoryVariable, ResponseVariable)**

```{r, message = FALSE, warning = FALSE}
thePlot(mtcars, cyl, mpg)
```

#### Multivariate
`thePlot` can handle up to 3 variables. You can visualize the relationship between an explanatory variable and a response variable grouped by a third variable. 
Notes: the third variable must be a categorical variable. 

**thePlot(mydata, ExplanatoryVariable, ResponseVariable, )**

```{r, message= FALSE, warning=FALSE}
thePlot(mtcars, am, mpg, vs)
```

## List of cases 
There are 10 scenarios in total. You can find the corresponding plot type of each scenario in the following table. 


